% arara: pdflatex: { synctex: yes }
% arara: makeindex: { style: ctuthesis }
% arara: bibtex

% The class takes all the key=value arguments that \ctusetup does,
% and a couple more: draft and oneside
\documentclass[twoside]{ctuthesis}

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{pgf}
\usepackage{subcaption}

\ctusetup{
	mainlanguage = english,
%	titlelanguage = czech,
%	mainlanguage = czech,
	otherlanguages = {slovak,english},
	title-czech = {Řízení humanoidního robota pomocí neuronových sítí},
	title-english = {Neural networks for humanoid robot control},
	%subtitle-czech = {Přístup posilovaného učení},
	%subtitle-english = {Reinforcement learning approach},
	doctype = B,
	faculty = F3,
	department-czech = {Katedra kybernetiky},
	department-english = {Department of Cybernetics},
	author = {Silvestr Stanko},
	supervisor = {Ing. Zdeněk Buk Ph.D.},
	,
	fieldofstudy-english = {Cybernetics and Robotics},
	subfieldofstudy-english = {Robotics},
	fieldofstudy-czech = {Kybernetika a Robotika},
	subfieldofstudy-czech = {Robotika},
	keywords-czech = {neuronové sítě, LSTM, posilované učení, Q-učení},
	keywords-english = {neural networks, LSTM, reinforcement learning, Q-learning},
	day = 24,
	month = 5,
	year = 2016,
	specification-file = {ctutest-zadani.pdf},
	%front-specification = true,
	front-list-of-figures = false,
	front-list-of-tables = false,
%	monochrome = true,
%	layout-short = true,
}

\ctuprocess

\addto\ctucaptionsczech{%
	\def\supervisorname{Vedoucí}%
	\def\subfieldofstudyname{Studijní program}%
}

\ctutemplateset{maketitle twocolumn default}{
	\begin{twocolumnfrontmatterpage}
		\ctutemplate{twocolumn.thanks}
		\ctutemplate{twocolumn.declaration}
		\ctutemplate{twocolumn.abstract.in.titlelanguage}
		\ctutemplate{twocolumn.abstract.in.secondlanguage}
		\ctutemplate{twocolumn.tableofcontents}
		\ctutemplate{twocolumn.listoffigures}
	\end{twocolumnfrontmatterpage}
}

% Theorem declarations, this is the reasonable default, anybody can do what they wish.
% If you prefer theorems in italics rather than slanted, use \theoremstyle{plainit}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{note}
\newtheorem*{remark*}{Remark}
\newtheorem{remark}[theorem]{Remark}

% Abstract in Czech
\begin{abstract-czech}
V této bakalářské práci nejprve popisuji několik odlišných druhů neuronových sítí, včetně rekurentních, a testuji je na simulaci chůze humanoidního robota. Dále popisuji  spojité, deterministické algoritmy posilovaného učení, vhodné pro řízení ve fyzikálním prostředí.

Tyto metody aplikuji na úlohách balancujícího inverzního kyvadla a dále na simulaci robota. Jak kyvadlo, tak robot jsou schopni udržovat rovnováhu, a to bez fyzikálního modelu či explicitní specifikace špatného či vhodného chování.
\end{abstract-czech}

% Abstract in English
\begin{abstract-english}
In this thesis I explore several different neural network architectures, including recurrent neural networks, and test them on a bipedal robot walking simulation. I further explore model-free continuous deterministic reinforcement learning, suitable for physical control tasks.

I apply these methods on a simpler inverse pendulum balancing tasks and later on the bipedal robot walking task. Both the pendulum and the robot are able to maintain balance without a physical model and explicitly specifying correct or incorrect behaviors.

\end{abstract-english}

% Acknowledgements / Podekovani
\begin{thanks}
I would like to thank my supervisor, Mr Buk for listening and help with server runs and my friend Tereza for help with language corrections.
\end{thanks}

% Declaration / Prohlaseni
\begin{declaration}
I declare that the presented work was developed independently and that I have listed all sources of information used within it in accordance with the methodical instructions for observing the ethical principles in the preparation of university thesis.

\vspace{2cm}

\noindent\rule{5cm}{0.4pt}

Silvestr Stanko

\vspace{1cm}

Prague, \ctufield{day}.~\monthinlanguage{title}~\ctufield{year}
\end{declaration}

% Only for testing purposes
\listfiles
\usepackage[pagewise]{lineno}
\usepackage{lipsum,blindtext}
\usepackage{mathrsfs} % provides \mathscr used in the ridiculous examples

\begin{document}

\maketitle

\input{introduction}

\input{robsim}

\input{supervised}

\input{reinforcement}

\input{ddpg}

\input{conclusion}


\appendix

\input{figures}

\bibliographystyle{alpha}%amsalpha

\bibliography{bakalarka}

\ctutemplate{specification.as.chapter}

\end{document}

